---
title: "Lab 02 - Plastic waste"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

From the graph, it looks like that African has the lowest plastic waste per capical on average. The distribution of plastic waste per capital for North America has the greatest variation. 

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
 geom_histogram(binwidth = 0.2) +
 labs (x="plastic_waste_per_captical", y="count", title="graph 1.1") +
 facet_wrap(~continent, nrow=7)

```


```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
     mapping = aes(x = plastic_waste_per_cap, 
                  color = continent, 
                  fill = continent)) +
  geom_density(alpha = 0.3)
```

### Exercise 3
Color and the fill can be specified by the name of the color, like "red". but the alpha refers to the transparency of all the colors that is presented in the graph.

### Exercise 4
violin plots also shows the density of each category. The botplots emphasize some extreme values which can not be directly seen in the violin plots.
```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
      mapping = aes(x = continent, 
                    y = plastic_waste_per_cap)) +
    geom_violin()
    
ggplot(data = plastic_waste, 
      mapping = aes(x = continent, 
                    y = plastic_waste_per_cap)) +
   geom_boxplot()
```


### Exercise 5

4.1. a slight positive correlation between mismanaged waste per capital and waste per capital.

```{r plastic-waste-mismanaged}
 ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste_per_cap,
                     y = plastic_waste_per_cap)) +
    geom_point()
```


### Exercise 6

4.2. It helps to visualize difference among continents and distinguish the correlation for each continent, but the points are still very concentrated and hard to look at.

```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste_per_cap, 
       y = plastic_waste_per_cap,color = continent,fill = continent)) +
   geom_point()
```

### Exercise 7

coastal population has slightly negative relationship with plastic waste per capital. Total population and plastic waste per capital has weaker associations in general. None of the pairs of variables appear to be storngly linearly associated.

```{r plastic-waste-population-total}
 ggplot(data = plastic_waste, 
        mapping = aes(x = total_pop, 
                     y = plastic_waste_per_cap,color = continent,fill = continent)) +
                     geom_point()
```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste, 
      mapping = aes(x = coastal_pop, 
                     y = plastic_waste_per_cap, color = continent,fill = continent)) +
   geom_point()
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
  
### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



